### 2022-12-07 output/01_exploratory/tables/bldg_val_results_table.tex
Created estimation tables

{
\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
\begin{tabular}{l*{4}{c}}
\toprule
                    &\multicolumn{1}{c}{\hspace{0.25cm}Building value}&\multicolumn{1}{c}{\hspace{0.25cm}Building value}&\multicolumn{1}{c}{\hspace{0.25cm}Building value}&\multicolumn{1}{c}{\hspace{0.25cm}Building value}\\
\midrule
judgment\_for\_plaintiff&   2434984.3\sym{***}&   1161294.0\sym{*}  &   1161294.0\sym{*}  &   1055231.1         \\
                    &      (4.14)         &      (2.56)         &      (2.56)         &      (0.46)         \\
\addlinespace
file\_year=2019      &                     &           0         &           0         &                     \\
                    &                     &         (.)         &         (.)         &                     \\
\addlinespace
file\_year=2020      &                     &    192394.9         &    192394.9         &                     \\
                    &                     &      (0.41)         &      (0.41)         &                     \\
\addlinespace
file\_year=2021      &                     &   1461400.9         &   1461400.9         &                     \\
                    &                     &      (0.80)         &      (0.80)         &                     \\
\addlinespace
Abington            &                     &           0         &           0         &                     \\
                    &                     &         (.)         &         (.)         &                     \\
\addlinespace
Acton               &                     &  -6165616.0         &  -6165616.0         &                     \\
                    &                     &     (-0.97)         &     (-0.97)         &                     \\
\addlinespace
Adams               &                     & -21444727.6\sym{***}& -21444727.6\sym{***}&                     \\
                    &                     &     (-5.94)         &     (-5.94)         &                     \\
\addlinespace
Agawam              &                     & -18038332.4\sym{***}& -18038332.4\sym{***}&                     \\
                    &                     &     (-3.80)         &     (-3.80)         &                     \\
\addlinespace
Amesbury            &                     & -19407326.1\sym{**} & -19407326.1\sym{**} &                     \\
                    &                     &     (-3.07)         &     (-3.07)         &                     \\
\addlinespace
Amherst             &                     & -11242459.5\sym{*}  & -11242459.5\sym{*}  &                     \\
                    &                     &     (-2.45)         &     (-2.45)         &                     \\
\addlinespace
Andover             &                     &  -2085030.0         &  -2085030.0         &                     \\
                    &                     &     (-0.60)         &     (-0.60)         &                     \\
\addlinespace
Athol               &                     & -21616109.3\sym{***}& -21616109.3\sym{***}&                     \\
                    &                     &     (-4.16)         &     (-4.16)         &                     \\
\addlinespace
Attleboro           &                     & -19494997.4\sym{***}& -19494997.4\sym{***}&                     \\
                    &                     &     (-5.39)         &     (-5.39)         &                     \\
\addlinespace
Auburn              &                     & -21471031.4\sym{***}& -21471031.4\sym{***}&                     \\
                    &                     &     (-3.67)         &     (-3.67)         &                     \\
\addlinespace
Bedford             &                     &   2478285.3         &   2478285.3         &                     \\
                    &                     &      (0.42)         &      (0.42)         &                     \\
\addlinespace
Belchertown         &                     & -20404418.7\sym{***}& -20404418.7\sym{***}&                     \\
                    &                     &     (-5.40)         &     (-5.40)         &                     \\
\addlinespace
Bellingham          &                     &  18138281.2\sym{**} &  18138281.2\sym{**} &                     \\
                    &                     &      (3.10)         &      (3.10)         &                     \\
\addlinespace
Beverly             &                     & -14079413.5\sym{***}& -14079413.5\sym{***}&                     \\
                    &                     &     (-4.85)         &     (-4.85)         &                     \\
\addlinespace
Billerica           &                     &   6526049.6         &   6526049.6         &                     \\
                    &                     &      (1.83)         &      (1.83)         &                     \\
\addlinespace
Braintree           &                     &  22784206.9\sym{***}&  22784206.9\sym{***}&                     \\
                    &                     &      (6.46)         &      (6.46)         &                     \\
\addlinespace
Brewster            &                     & -20607212.4\sym{**} & -20607212.4\sym{**} &                     \\
                    &                     &     (-3.26)         &     (-3.26)         &                     \\
\addlinespace
Bridgewater         &                     &   9388781.6\sym{**} &   9388781.6\sym{**} &                     \\
                    &                     &      (2.95)         &      (2.95)         &                     \\
\addlinespace
Brockton            &                     & -17475780.0\sym{***}& -17475780.0\sym{***}&                     \\
                    &                     &     (-7.32)         &     (-7.32)         &                     \\
\addlinespace
Brookline           &                     & -16179317.8\sym{**} & -16179317.8\sym{**} &                     \\
                    &                     &     (-2.77)         &     (-2.77)         &                     \\
\addlinespace
Cambridge           &                     &  26938732.3\sym{***}&  26938732.3\sym{***}&                     \\
                    &                     &      (7.34)         &      (7.34)         &                     \\
\addlinespace
Canton              &                     &   3432893.5         &   3432893.5         &                     \\
                    &                     &      (0.99)         &      (0.99)         &                     \\
\addlinespace
Chelmsford          &                     &  -4604628.5         &  -4604628.5         &                     \\
                    &                     &     (-0.73)         &     (-0.73)         &                     \\
\addlinespace
Chelsea             &                     &  -3808897.8         &  -3808897.8         &                     \\
                    &                     &     (-0.88)         &     (-0.88)         &                     \\
\addlinespace
Chicopee            &                     & -19004695.9\sym{***}& -19004695.9\sym{***}&                     \\
                    &                     &     (-6.87)         &     (-6.87)         &                     \\
\addlinespace
Clinton             &                     & -21059441.8\sym{***}& -21059441.8\sym{***}&                     \\
                    &                     &     (-4.43)         &     (-4.43)         &                     \\
\addlinespace
Concord             &                     &  29495396.8\sym{***}&  29495396.8\sym{***}&                     \\
                    &                     &      (5.04)         &      (5.04)         &                     \\
\addlinespace
Danvers             &                     &  -5577347.4         &  -5577347.4         &                     \\
                    &                     &     (-1.29)         &     (-1.29)         &                     \\
\addlinespace
Dracut              &                     & -19485987.8\sym{***}& -19485987.8\sym{***}&                     \\
                    &                     &     (-4.52)         &     (-4.52)         &                     \\
\addlinespace
Dudley              &                     & -21722608.3\sym{***}& -21722608.3\sym{***}&                     \\
                    &                     &     (-3.96)         &     (-3.96)         &                     \\
\addlinespace
Duxbury             &                     & -15198237.7\sym{**} & -15198237.7\sym{**} &                     \\
                    &                     &     (-2.77)         &     (-2.77)         &                     \\
\addlinespace
East Wareham        &                     & -15344281.4\sym{**} & -15344281.4\sym{**} &                     \\
                    &                     &     (-2.62)         &     (-2.62)         &                     \\
\addlinespace
Everett             &                     &  -7534870.7\sym{*}  &  -7534870.7\sym{*}  &                     \\
                    &                     &     (-2.05)         &     (-2.05)         &                     \\
\addlinespace
Fairhaven           &                     & -21231090.0\sym{***}& -21231090.0\sym{***}&                     \\
                    &                     &     (-5.71)         &     (-5.71)         &                     \\
\addlinespace
Fall River          &                     & -18210525.7\sym{***}& -18210525.7\sym{***}&                     \\
                    &                     &     (-7.32)         &     (-7.32)         &                     \\
\addlinespace
Feeding Hills       &                     & -18650234.9\sym{***}& -18650234.9\sym{***}&                     \\
                    &                     &     (-5.23)         &     (-5.23)         &                     \\
\addlinespace
Fitchburg           &                     & -20960701.9\sym{***}& -20960701.9\sym{***}&                     \\
                    &                     &     (-8.30)         &     (-8.30)         &                     \\
\addlinespace
Foxboro             &                     &  20690798.8\sym{***}&  20690798.8\sym{***}&                     \\
                    &                     &      (4.35)         &      (4.35)         &                     \\
\addlinespace
Foxborough          &                     &  19142493.9\sym{**} &  19142493.9\sym{**} &                     \\
                    &                     &      (3.03)         &      (3.03)         &                     \\
\addlinespace
Framingham          &                     &  -2290752.1         &  -2290752.1         &                     \\
                    &                     &     (-0.83)         &     (-0.83)         &                     \\
\addlinespace
Franklin            &                     &  -4710134.2         &  -4710134.2         &                     \\
                    &                     &     (-1.25)         &     (-1.25)         &                     \\
\addlinespace
Gardner             &                     & -18492792.1\sym{***}& -18492792.1\sym{***}&                     \\
                    &                     &     (-5.24)         &     (-5.24)         &                     \\
\addlinespace
Gloucester          &                     & -14776186.1\sym{***}& -14776186.1\sym{***}&                     \\
                    &                     &     (-4.80)         &     (-4.80)         &                     \\
\addlinespace
Grafton             &                     & -11539053.6         & -11539053.6         &                     \\
                    &                     &     (-1.82)         &     (-1.82)         &                     \\
\addlinespace
Greenfield          &                     & -19186461.0\sym{***}& -19186461.0\sym{***}&                     \\
                    &                     &     (-4.88)         &     (-4.88)         &                     \\
\addlinespace
Hanson              &                     & -21517852.4\sym{***}& -21517852.4\sym{***}&                     \\
                    &                     &     (-3.40)         &     (-3.40)         &                     \\
\addlinespace
Haverhill           &                     & -18493946.4\sym{***}& -18493946.4\sym{***}&                     \\
                    &                     &     (-6.52)         &     (-6.52)         &                     \\
\addlinespace
Holyoke             &                     & -19922013.6\sym{***}& -19922013.6\sym{***}&                     \\
                    &                     &     (-7.02)         &     (-7.02)         &                     \\
\addlinespace
Hudson              &                     & -21242768.8\sym{***}& -21242768.8\sym{***}&                     \\
                    &                     &     (-3.63)         &     (-3.63)         &                     \\
\addlinespace
Hull                &                     & -14403896.8\sym{***}& -14403896.8\sym{***}&                     \\
                    &                     &     (-3.67)         &     (-3.67)         &                     \\
\addlinespace
Hyannis             &                     & -19591284.6\sym{***}& -19591284.6\sym{***}&                     \\
                    &                     &     (-4.27)         &     (-4.27)         &                     \\
\addlinespace
Indian Orchard      &                     & -20946341.5\sym{***}& -20946341.5\sym{***}&                     \\
                    &                     &     (-7.04)         &     (-7.04)         &                     \\
\addlinespace
Ipswich             &                     & -19517731.6\sym{***}& -19517731.6\sym{***}&                     \\
                    &                     &     (-3.94)         &     (-3.94)         &                     \\
\addlinespace
Lakeville           &                     & -17182100.0\sym{***}& -17182100.0\sym{***}&                     \\
                    &                     &     (-3.88)         &     (-3.88)         &                     \\
\addlinespace
Lawrence            &                     & -18777158.2\sym{***}& -18777158.2\sym{***}&                     \\
                    &                     &     (-7.91)         &     (-7.91)         &                     \\
\addlinespace
Leominster          &                     & -17218870.0\sym{***}& -17218870.0\sym{***}&                     \\
                    &                     &     (-5.85)         &     (-5.85)         &                     \\
\addlinespace
Lowell              &                     & -15677026.1\sym{***}& -15677026.1\sym{***}&                     \\
                    &                     &     (-6.66)         &     (-6.66)         &                     \\
\addlinespace
Ludlow              &                     & -20818614.1\sym{***}& -20818614.1\sym{***}&                     \\
                    &                     &     (-5.20)         &     (-5.20)         &                     \\
\addlinespace
Lunenburg           &                     & -21732251.2\sym{***}& -21732251.2\sym{***}&                     \\
                    &                     &     (-3.44)         &     (-3.44)         &                     \\
\addlinespace
Lynn                &                     & -18818313.7\sym{***}& -18818313.7\sym{***}&                     \\
                    &                     &     (-7.06)         &     (-7.06)         &                     \\
\addlinespace
Lynnfield           &                     &  -3055971.2         &  -3055971.2         &                     \\
                    &                     &     (-0.48)         &     (-0.48)         &                     \\
\addlinespace
Malden              &                     &    998329.8         &    998329.8         &                     \\
                    &                     &      (0.35)         &      (0.35)         &                     \\
\addlinespace
Mansfield           &                     & -13438414.8\sym{***}& -13438414.8\sym{***}&                     \\
                    &                     &     (-3.43)         &     (-3.43)         &                     \\
\addlinespace
Marblehead          &                     & -20700912.8\sym{***}& -20700912.8\sym{***}&                     \\
                    &                     &     (-4.36)         &     (-4.36)         &                     \\
\addlinespace
Marshfield          &                     & -20789134.1\sym{***}& -20789134.1\sym{***}&                     \\
                    &                     &     (-5.80)         &     (-5.80)         &                     \\
\addlinespace
Mashpee             &                     & -19830247.1\sym{***}& -19830247.1\sym{***}&                     \\
                    &                     &     (-3.39)         &     (-3.39)         &                     \\
\addlinespace
Methuen             &                     & -15000192.3\sym{***}& -15000192.3\sym{***}&                     \\
                    &                     &     (-5.53)         &     (-5.53)         &                     \\
\addlinespace
Middleboro          &                     & -12265582.7\sym{***}& -12265582.7\sym{***}&                     \\
                    &                     &     (-3.94)         &     (-3.94)         &                     \\
\addlinespace
Milford             &                     &  -9017182.4\sym{*}  &  -9017182.4\sym{*}  &                     \\
                    &                     &     (-2.34)         &     (-2.34)         &                     \\
\addlinespace
Millbury            &                     & -18658188.7\sym{***}& -18658188.7\sym{***}&                     \\
                    &                     &     (-3.59)         &     (-3.59)         &                     \\
\addlinespace
Needham             &                     &  39077459.2\sym{***}&  39077459.2\sym{***}&                     \\
                    &                     &      (9.08)         &      (9.08)         &                     \\
\addlinespace
New Bedford         &                     & -20447207.1\sym{***}& -20447207.1\sym{***}&                     \\
                    &                     &     (-8.55)         &     (-8.55)         &                     \\
\addlinespace
Newburyport         &                     & -17619838.9\sym{***}& -17619838.9\sym{***}&                     \\
                    &                     &     (-4.30)         &     (-4.30)         &                     \\
\addlinespace
North Adams         &                     & -20332323.4\sym{***}& -20332323.4\sym{***}&                     \\
                    &                     &     (-5.28)         &     (-5.28)         &                     \\
\addlinespace
North Andover       &                     &  -4927981.2         &  -4927981.2         &                     \\
                    &                     &     (-1.52)         &     (-1.52)         &                     \\
\addlinespace
North Attleboro     &                     & -20284380.8\sym{***}& -20284380.8\sym{***}&                     \\
                    &                     &     (-5.45)         &     (-5.45)         &                     \\
\addlinespace
North Billerica     &                     &  -8556369.2         &  -8556369.2         &                     \\
                    &                     &     (-1.80)         &     (-1.80)         &                     \\
\addlinespace
North Dartmouth     &                     & -13208231.2\sym{*}  & -13208231.2\sym{*}  &                     \\
                    &                     &     (-2.09)         &     (-2.09)         &                     \\
\addlinespace
Northampton         &                     & -20101965.1\sym{***}& -20101965.1\sym{***}&                     \\
                    &                     &     (-4.40)         &     (-4.40)         &                     \\
\addlinespace
Northborough        &                     &  40356948.8\sym{***}&  40356948.8\sym{***}&                     \\
                    &                     &      (8.49)         &      (8.49)         &                     \\
\addlinespace
Norton              &                     &  -6420841.7         &  -6420841.7         &                     \\
                    &                     &     (-1.49)         &     (-1.49)         &                     \\
\addlinespace
Norwood             &                     &  94746120.3\sym{***}&  94746120.3\sym{***}&                     \\
                    &                     &     (29.37)         &     (29.37)         &                     \\
\addlinespace
Oxford              &                     &  -9152764.4         &  -9152764.4         &                     \\
                    &                     &     (-1.76)         &     (-1.76)         &                     \\
\addlinespace
Peabody             &                     &   9805861.1\sym{***}&   9805861.1\sym{***}&                     \\
                    &                     &      (3.68)         &      (3.68)         &                     \\
\addlinespace
Pittsfield          &                     & -20746717.5\sym{***}& -20746717.5\sym{***}&                     \\
                    &                     &     (-7.86)         &     (-7.86)         &                     \\
\addlinespace
Plymouth            &                     & -20826306.6\sym{***}& -20826306.6\sym{***}&                     \\
                    &                     &     (-4.65)         &     (-4.65)         &                     \\
\addlinespace
Quincy              &                     &  -1743417.5         &  -1743417.5         &                     \\
                    &                     &     (-0.44)         &     (-0.44)         &                     \\
\addlinespace
Randolph            &                     &  -2226994.8         &  -2226994.8         &                     \\
                    &                     &     (-0.79)         &     (-0.79)         &                     \\
\addlinespace
Revere              &                     &   -159168.5         &   -159168.5         &                     \\
                    &                     &     (-0.03)         &     (-0.03)         &                     \\
\addlinespace
Rockland            &                     & -20101861.1\sym{***}& -20101861.1\sym{***}&                     \\
                    &                     &     (-6.55)         &     (-6.55)         &                     \\
\addlinespace
Salem               &                     & -16857836.8\sym{***}& -16857836.8\sym{***}&                     \\
                    &                     &     (-5.79)         &     (-5.79)         &                     \\
\addlinespace
Sandwich            &                     & -20722231.4\sym{***}& -20722231.4\sym{***}&                     \\
                    &                     &     (-3.54)         &     (-3.54)         &                     \\
\addlinespace
Saugus              &                     &   -340363.5         &   -340363.5         &                     \\
                    &                     &     (-0.10)         &     (-0.10)         &                     \\
\addlinespace
Seekonk             &                     &  17681397.2\sym{***}&  17681397.2\sym{***}&                     \\
                    &                     &      (4.89)         &      (4.89)         &                     \\
\addlinespace
Shirley             &                     & -21737007.4\sym{***}& -21737007.4\sym{***}&                     \\
                    &                     &     (-4.90)         &     (-4.90)         &                     \\
\addlinespace
Shrewsbury          &                     & -12117923.8\sym{*}  & -12117923.8\sym{*}  &                     \\
                    &                     &     (-2.45)         &     (-2.45)         &                     \\
\addlinespace
Somerville          &                     & -19566426.9\sym{***}& -19566426.9\sym{***}&                     \\
                    &                     &     (-3.77)         &     (-3.77)         &                     \\
\addlinespace
South Hadley        &                     & -20340123.7\sym{***}& -20340123.7\sym{***}&                     \\
                    &                     &     (-4.97)         &     (-4.97)         &                     \\
\addlinespace
Southbridge         &                     & -21059479.9\sym{***}& -21059479.9\sym{***}&                     \\
                    &                     &     (-7.09)         &     (-7.09)         &                     \\
\addlinespace
Southwick           &                     & -20440194.9\sym{***}& -20440194.9\sym{***}&                     \\
                    &                     &     (-3.73)         &     (-3.73)         &                     \\
\addlinespace
Spencer             &                     & -21062533.5\sym{***}& -21062533.5\sym{***}&                     \\
                    &                     &     (-5.26)         &     (-5.26)         &                     \\
\addlinespace
Springfield         &                     & -17446784.4\sym{***}& -17446784.4\sym{***}&                     \\
                    &                     &     (-7.56)         &     (-7.56)         &                     \\
\addlinespace
Stoughton           &                     & -11389546.7\sym{***}& -11389546.7\sym{***}&                     \\
                    &                     &     (-3.83)         &     (-3.83)         &                     \\
\addlinespace
Swampscott          &                     &  -4547859.6         &  -4547859.6         &                     \\
                    &                     &     (-1.08)         &     (-1.08)         &                     \\
\addlinespace
Taunton             &                     & -20276710.6\sym{***}& -20276710.6\sym{***}&                     \\
                    &                     &     (-7.44)         &     (-7.44)         &                     \\
\addlinespace
Tewksbury           &                     &   5281791.2         &   5281791.2         &                     \\
                    &                     &      (1.50)         &      (1.50)         &                     \\
\addlinespace
Three Rivers        &                     & -21263534.4\sym{***}& -21263534.4\sym{***}&                     \\
                    &                     &     (-3.88)         &     (-3.88)         &                     \\
\addlinespace
Tyngsboro           &                     & -19043379.7\sym{***}& -19043379.7\sym{***}&                     \\
                    &                     &     (-3.47)         &     (-3.47)         &                     \\
\addlinespace
Wakefield           &                     & -12951456.3\sym{**} & -12951456.3\sym{**} &                     \\
                    &                     &     (-3.24)         &     (-3.24)         &                     \\
\addlinespace
Walpole             &                     & -10254842.1\sym{*}  & -10254842.1\sym{*}  &                     \\
                    &                     &     (-2.24)         &     (-2.24)         &                     \\
\addlinespace
Waltham             &                     &  -4458163.9         &  -4458163.9         &                     \\
                    &                     &     (-1.57)         &     (-1.57)         &                     \\
\addlinespace
Ware                &                     & -21385935.2\sym{***}& -21385935.2\sym{***}&                     \\
                    &                     &     (-5.84)         &     (-5.84)         &                     \\
\addlinespace
Watertown           &                     &  14594615.7\sym{**} &  14594615.7\sym{**} &                     \\
                    &                     &      (2.81)         &      (2.81)         &                     \\
\addlinespace
Webster             &                     & -20767336.3\sym{***}& -20767336.3\sym{***}&                     \\
                    &                     &     (-4.19)         &     (-4.19)         &                     \\
\addlinespace
West Springfield    &                     & -20814715.6\sym{***}& -20814715.6\sym{***}&                     \\
                    &                     &     (-6.16)         &     (-6.16)         &                     \\
\addlinespace
Westborough         &                     &   4823814.7         &   4823814.7         &                     \\
                    &                     &      (1.40)         &      (1.40)         &                     \\
\addlinespace
Westwood            &                     &   3245897.8         &   3245897.8         &                     \\
                    &                     &      (0.56)         &      (0.56)         &                     \\
\addlinespace
Weymouth            &                     &  -4254268.3         &  -4254268.3         &                     \\
                    &                     &     (-1.01)         &     (-1.01)         &                     \\
\addlinespace
Whitinsville        &                     & -21120051.2\sym{***}& -21120051.2\sym{***}&                     \\
                    &                     &     (-3.34)         &     (-3.34)         &                     \\
\addlinespace
Whitman             &                     & -19787518.2\sym{***}& -19787518.2\sym{***}&                     \\
                    &                     &     (-4.83)         &     (-4.83)         &                     \\
\addlinespace
Winchendon          &                     & -21661279.7\sym{***}& -21661279.7\sym{***}&                     \\
                    &                     &     (-3.95)         &     (-3.95)         &                     \\
\addlinespace
Woburn              &                     &  42856970.1\sym{***}&  42856970.1\sym{***}&                     \\
                    &                     &      (9.65)         &      (9.65)         &                     \\
\addlinespace
Worcester           &                     & -19269002.4\sym{***}& -19269002.4\sym{***}&                     \\
                    &                     &     (-8.12)         &     (-8.12)         &                     \\
\addlinespace
group(property\_address\_city file\_year)=1&                     &                     &                     &           0         \\
                    &                     &                     &                     &         (.)         \\
\addlinespace
group(property\_address\_city file\_year)=2&                     &                     &                     & -21747387.2\sym{**} \\
                    &                     &                     &                     &     (-3.04)         \\
\addlinespace
group(property\_address\_city file\_year)=3&                     &                     &                     & -16553233.1         \\
                    &                     &                     &                     &     (-1.57)         \\
\addlinespace
group(property\_address\_city file\_year)=7&                     &                     &                     & -31817166.7\sym{***}\\
                    &                     &                     &                     &     (-4.84)         \\
\addlinespace
group(property\_address\_city file\_year)=8&                     &                     &                     & -31572134.4\sym{***}\\
                    &                     &                     &                     &     (-4.79)         \\
\addlinespace
group(property\_address\_city file\_year)=9&                     &                     &                     & -28362311.8\sym{***}\\
                    &                     &                     &                     &     (-4.12)         \\
\addlinespace
group(property\_address\_city file\_year)=11&                     &                     &                     & -29517698.0\sym{***}\\
                    &                     &                     &                     &     (-4.40)         \\
\addlinespace
group(property\_address\_city file\_year)=12&                     &                     &                     & -21429968.1\sym{**} \\
                    &                     &                     &                     &     (-3.13)         \\
\addlinespace
group(property\_address\_city file\_year)=13&                     &                     &                     &  -7726729.5         \\
                    &                     &                     &                     &     (-0.93)         \\
\addlinespace
group(property\_address\_city file\_year)=14&                     &                     &                     & -16546877.7         \\
                    &                     &                     &                     &     (-1.92)         \\
\addlinespace
group(property\_address\_city file\_year)=23&                     &                     &                     & -31739739.1\sym{***}\\
                    &                     &                     &                     &     (-4.83)         \\
\addlinespace
group(property\_address\_city file\_year)=24&                     &                     &                     & -29812227.4\sym{***}\\
                    &                     &                     &                     &     (-4.49)         \\
\addlinespace
group(property\_address\_city file\_year)=26&                     &                     &                     & -31616757.7\sym{***}\\
                    &                     &                     &                     &     (-4.81)         \\
\addlinespace
group(property\_address\_city file\_year)=31&                     &                     &                     &  -7667441.0         \\
                    &                     &                     &                     &     (-0.74)         \\
\addlinespace
group(property\_address\_city file\_year)=33&                     &                     &                     & -31058487.8\sym{***}\\
                    &                     &                     &                     &     (-4.72)         \\
\addlinespace
group(property\_address\_city file\_year)=34&                     &                     &                     & -29958013.6\sym{***}\\
                    &                     &                     &                     &     (-4.53)         \\
\addlinespace
group(property\_address\_city file\_year)=35&                     &                     &                     &   7817837.2         \\
                    &                     &                     &                     &      (0.33)         \\
\addlinespace
group(property\_address\_city file\_year)=39&                     &                     &                     & -23427539.3\sym{***}\\
                    &                     &                     &                     &     (-3.45)         \\
\addlinespace
group(property\_address\_city file\_year)=40&                     &                     &                     & -26490197.7\sym{***}\\
                    &                     &                     &                     &     (-3.84)         \\
\addlinespace
group(property\_address\_city file\_year)=42&                     &                     &                     &  -1787415.9         \\
                    &                     &                     &                     &     (-0.24)         \\
\addlinespace
group(property\_address\_city file\_year)=43&                     &                     &                     &  -7367293.9         \\
                    &                     &                     &                     &     (-0.88)         \\
\addlinespace
group(property\_address\_city file\_year)=53&                     &                     &                     &  12651738.5         \\
                    &                     &                     &                     &      (1.56)         \\
\addlinespace
group(property\_address\_city file\_year)=54&                     &                     &                     & -30931191.8\sym{***}\\
                    &                     &                     &                     &     (-4.68)         \\
\addlinespace
group(property\_address\_city file\_year)=56&                     &                     &                     &   -941258.6         \\
                    &                     &                     &                     &     (-0.12)         \\
\addlinespace
group(property\_address\_city file\_year)=58&                     &                     &                     & -27434049.1\sym{***}\\
                    &                     &                     &                     &     (-4.15)         \\
\addlinespace
group(property\_address\_city file\_year)=59&                     &                     &                     & -28035133.5\sym{***}\\
                    &                     &                     &                     &     (-4.23)         \\
\addlinespace
group(property\_address\_city file\_year)=60&                     &                     &                     & -26482084.7\sym{***}\\
                    &                     &                     &                     &     (-3.56)         \\
\addlinespace
group(property\_address\_city file\_year)=66&                     &                     &                     &  16595560.5         \\
                    &                     &                     &                     &      (1.21)         \\
\addlinespace
group(property\_address\_city file\_year)=67&                     &                     &                     &  -3516394.1         \\
                    &                     &                     &                     &     (-0.44)         \\
\addlinespace
group(property\_address\_city file\_year)=68&                     &                     &                     & -15346166.3         \\
                    &                     &                     &                     &     (-1.61)         \\
\addlinespace
group(property\_address\_city file\_year)=73&                     &                     &                     & -14757425.6\sym{*}  \\
                    &                     &                     &                     &     (-2.24)         \\
\addlinespace
group(property\_address\_city file\_year)=74&                     &                     &                     & -25535691.0\sym{***}\\
                    &                     &                     &                     &     (-3.40)         \\
\addlinespace
group(property\_address\_city file\_year)=75&                     &                     &                     &  -4233310.1         \\
                    &                     &                     &                     &     (-0.46)         \\
\addlinespace
group(property\_address\_city file\_year)=83&                     &                     &                     & -29174821.6\sym{***}\\
                    &                     &                     &                     &     (-4.40)         \\
\addlinespace
group(property\_address\_city file\_year)=84&                     &                     &                     & -31372814.9\sym{***}\\
                    &                     &                     &                     &     (-4.76)         \\
\addlinespace
group(property\_address\_city file\_year)=88&                     &                     &                     &  19157275.7         \\
                    &                     &                     &                     &      (1.72)         \\
\addlinespace
group(property\_address\_city file\_year)=92&                     &                     &                     & -15712195.5         \\
                    &                     &                     &                     &     (-1.86)         \\
\addlinespace
group(property\_address\_city file\_year)=99&                     &                     &                     & -29653470.5\sym{***}\\
                    &                     &                     &                     &     (-4.43)         \\
\addlinespace
group(property\_address\_city file\_year)=100&                     &                     &                     & -32025375.2\sym{***}\\
                    &                     &                     &                     &     (-4.86)         \\
\addlinespace
group(property\_address\_city file\_year)=103&                     &                     &                     & -25516156.4\sym{***}\\
                    &                     &                     &                     &     (-3.59)         \\
\addlinespace
group(property\_address\_city file\_year)=113&                     &                     &                     & -25490007.7\sym{***}\\
                    &                     &                     &                     &     (-3.43)         \\
\addlinespace
group(property\_address\_city file\_year)=120&                     &                     &                     & -17660394.5\sym{*}  \\
                    &                     &                     &                     &     (-1.98)         \\
\addlinespace
group(property\_address\_city file\_year)=121&                     &                     &                     & -31937592.6\sym{***}\\
                    &                     &                     &                     &     (-4.85)         \\
\addlinespace
group(property\_address\_city file\_year)=122&                     &                     &                     & -30621970.7\sym{***}\\
                    &                     &                     &                     &     (-4.62)         \\
\addlinespace
group(property\_address\_city file\_year)=123&                     &                     &                     & -28326993.2\sym{***}\\
                    &                     &                     &                     &     (-4.29)         \\
\addlinespace
group(property\_address\_city file\_year)=125&                     &                     &                     & -29342045.6\sym{***}\\
                    &                     &                     &                     &     (-4.42)         \\
\addlinespace
group(property\_address\_city file\_year)=126&                     &                     &                     & -28176986.1\sym{***}\\
                    &                     &                     &                     &     (-4.09)         \\
\addlinespace
group(property\_address\_city file\_year)=127&                     &                     &                     & -31295574.7\sym{***}\\
                    &                     &                     &                     &     (-4.76)         \\
\addlinespace
group(property\_address\_city file\_year)=128&                     &                     &                     & -31064464.4\sym{***}\\
                    &                     &                     &                     &     (-4.72)         \\
\addlinespace
group(property\_address\_city file\_year)=132&                     &                     &                     &  10388032.0         \\
                    &                     &                     &                     &      (1.57)         \\
\addlinespace
group(property\_address\_city file\_year)=134&                     &                     &                     &   9032122.0         \\
                    &                     &                     &                     &      (1.36)         \\
\addlinespace
group(property\_address\_city file\_year)=135&                     &                     &                     & -12412590.3         \\
                    &                     &                     &                     &     (-1.78)         \\
\addlinespace
group(property\_address\_city file\_year)=136&                     &                     &                     & -19582760.6\sym{*}  \\
                    &                     &                     &                     &     (-2.57)         \\
\addlinespace
group(property\_address\_city file\_year)=137&                     &                     &                     &  -8576722.7         \\
                    &                     &                     &                     &     (-0.98)         \\
\addlinespace
group(property\_address\_city file\_year)=138&                     &                     &                     & -28607583.4\sym{***}\\
                    &                     &                     &                     &     (-4.29)         \\
\addlinespace
group(property\_address\_city file\_year)=142&                     &                     &                     & -25588880.8\sym{***}\\
                    &                     &                     &                     &     (-3.77)         \\
\addlinespace
group(property\_address\_city file\_year)=143&                     &                     &                     & -23441624.9\sym{***}\\
                    &                     &                     &                     &     (-3.39)         \\
\addlinespace
group(property\_address\_city file\_year)=144&                     &                     &                     & -21884245.6\sym{**} \\
                    &                     &                     &                     &     (-2.77)         \\
\addlinespace
group(property\_address\_city file\_year)=147&                     &                     &                     & -29352983.9\sym{***}\\
                    &                     &                     &                     &     (-4.39)         \\
\addlinespace
group(property\_address\_city file\_year)=153&                     &                     &                     & -31841831.8\sym{***}\\
                    &                     &                     &                     &     (-4.84)         \\
\addlinespace
group(property\_address\_city file\_year)=156&                     &                     &                     & -28639093.1\sym{***}\\
                    &                     &                     &                     &     (-4.34)         \\
\addlinespace
group(property\_address\_city file\_year)=164&                     &                     &                     & -30086286.3\sym{***}\\
                    &                     &                     &                     &     (-4.55)         \\
\addlinespace
group(property\_address\_city file\_year)=167&                     &                     &                     & -31563212.8\sym{***}\\
                    &                     &                     &                     &     (-4.80)         \\
\addlinespace
group(property\_address\_city file\_year)=168&                     &                     &                     & -26148336.2\sym{***}\\
                    &                     &                     &                     &     (-3.44)         \\
\addlinespace
group(property\_address\_city file\_year)=169&                     &                     &                     & -21888879.5\sym{*}  \\
                    &                     &                     &                     &     (-2.50)         \\
\addlinespace
group(property\_address\_city file\_year)=171&                     &                     &                     & -29740224.9\sym{***}\\
                    &                     &                     &                     &     (-4.49)         \\
\addlinespace
group(property\_address\_city file\_year)=172&                     &                     &                     & -31399983.4\sym{***}\\
                    &                     &                     &                     &     (-4.78)         \\
\addlinespace
group(property\_address\_city file\_year)=173&                     &                     &                     & -30775755.6\sym{***}\\
                    &                     &                     &                     &     (-4.61)         \\
\addlinespace
group(property\_address\_city file\_year)=174&                     &                     &                     & -29867637.5\sym{***}\\
                    &                     &                     &                     &     (-4.51)         \\
\addlinespace
group(property\_address\_city file\_year)=179&                     &                     &                     & -29450518.0\sym{***}\\
                    &                     &                     &                     &     (-4.43)         \\
\addlinespace
group(property\_address\_city file\_year)=180&                     &                     &                     & -24582985.6\sym{***}\\
                    &                     &                     &                     &     (-3.56)         \\
\addlinespace
group(property\_address\_city file\_year)=182&                     &                     &                     & -29062568.7\sym{***}\\
                    &                     &                     &                     &     (-4.41)         \\
\addlinespace
group(property\_address\_city file\_year)=183&                     &                     &                     & -28961589.8\sym{***}\\
                    &                     &                     &                     &     (-4.39)         \\
\addlinespace

>>>>

{
\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
\begin{tabular}{l*{4}{c}}
\toprule
                    &\multicolumn{1}{c}{\hspace{0.25cm}Building value}&\multicolumn{1}{c}{\hspace{0.25cm}Building value}&\multicolumn{1}{c}{\hspace{0.25cm}Building value}&\multicolumn{1}{c}{\hspace{0.25cm}Building value}\\
                    &        b/se&        b/se&        b/se&        b/se\\
\midrule
judgment\_for\_plaintiff& 2434984.290& 1161293.951& 1161293.951& 1055231.099\\
                    & (588147.83)& (453836.79)& (453836.79)&(2319051.94)\\
\midrule
Observations        &        5567&        5567&        5567&        5567\\
\bottomrule
\end{tabular}
}
